\Title

### 2023-01-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

This paper proposes additional experiments on a recent model of spiking neuron with heterogeneous synaptic delays.

>>>>

The present paper proposes additional experiments on a recent model of spiking neurons with heterogeneous synaptic delays (i.e. time between the arrival of an afferent spike at a specific synapse and the contribution of the associated postsynaptic potential to the neuron's soma). This model was trained to solve a motion detection task on a synthetic event-based dataset. Once trained, its event-driven computations could be reduced drastically through the pruning of synapses, while maintaining top performance for classification. This showed that we may use the precise timing of spikes to enhance neural computations. In the different kernels obtained after training, one could observe spiking motifs linked to the different motion directions
